A Decision Procedure for (Co)datatypes in SMT Solvers

### 2014-12-17 tex/codatadp.tex
more

\begin{table*}[tbh!]
\normalsize
\begin{center}\begin{tabular}{l@{\kern1.5em}c@{\kern.5em}c@{\kern.5em}c@{\kern1.5em}c}
  & \HD{Distro} & \HD{AFP} & \HD{\gandl} & All
\\[1pt] %%% TYPESETTING HACK
\midrule
%$\enatT$
\\[-9pt] %%% TYPESETTING HACK
No (co)datatypes
  & 401 & 922 & \phantom{0}39 & 1122 \\
Codatatypes without bisimilarity
  & 410 & 936 & \phantom{0}45 & 1136 \\
Codatatypes with bisimilarity
  & 411 & 939 & \phantom{0}48 & 1139 \\
Datatypes without cyclicity
  & 415 & 947 & \phantom{0}43 & 1147 \\
Datatypes with cyclicity
  & 418 & 953 & \phantom{0}44 & 1153 \\
Full (co)datatypes
  & 440 & 970 & \phantom{0}49 & 1170 \\[\jot]
Total number of goals
  & 879 & 2974\phantom{0} & 117 & 3970
\end{tabular}\end{center}
\caption{\,Number of solved goals for the three benchmark suites}
\label{tab:bench}
\end{table*}

@@

The results are summarized in Table~\ref{tab:bench}. The decision procedure
makes a difference across all theories, and an overall difference of
\BAD{4.7\%}. Moreover, every aspect of the procedure, including the more
expensive rules, make a contribution. What is not visible in the table, but
readily available when looking at the raw data \cite{our-eval-data}, is that
the stronger decision procedures subsume the weaker ones. In the context of
Sledgehammer, the power of interpreted (co)datatype is comparable with that of
arithmetic \cite{blanchette-et-al-2013-smt}.

>>>>

\begin{table*}[tbh!]
\normalsize
\begin{center}\begin{tabular}{l@{\kern1.5em}c@{\kern.5em}c@{\kern.5em}c@{\kern1.5em}c}
  & \HD{Distro} & \HD{AFP} & \HD{\gandl} & All
\\[1pt] %%% TYPESETTING HACK
\midrule
%$\enatT$
\\[-9pt] %%% TYPESETTING HACK
No (co)datatypes
  & 221 & 760 & \phantom{0}36 & 1017 \\
Datatypes without cyclicity
  & 227 & 765 & \phantom{0}36 & 1028 \\
Datatypes with cyclicity
  & 227 & 771 & \phantom{0}36 & 1034 \\
Codatatypes without bisimilarity
  & 217 & 787 & \phantom{0}34 & 1038 \\
Codatatypes with bisimilarity
  & 218 & 787 & \phantom{0}36 & 1041 \\
Full (co)datatypes
  & 224 & 798 & \phantom{0}36 & 1058 \\[\jot]
Total number of goals
  & 879 & 2974\phantom{0} & 117 & 3970
\end{tabular}\end{center}
\caption{\,Number of solved goals for the three benchmark suites}
\label{tab:bench}
\end{table*}

@@

The results are summarized in Table~\ref{tab:bench}. The decision procedure
makes a difference across all theories, and an overall difference of
\BAD{4.7\%}. Moreover, every aspect of the procedure, including the more
expensive rules, make a contribution. \textbf{NOT TRUE}: What is not visible in the table, but
readily available when looking at the raw data \cite{our-eval-data}, is that
the stronger decision procedures subsume the weaker ones. In the context of
Sledgehammer, the power of interpreted (co)datatype is comparable with that of
arithmetic \cite{blanchette-et-al-2013-smt}.
